\documentclass[12pt]{article}
\usepackage{array}
\usepackage{amsmath}
\usepackage{mathtools}
\usepackage{textcomp, gensymb}
\usepackage{graphicx}
\usepackage{float}
\usepackage{caption}
\usepackage{enumitem}
\usepackage[margin=1in]{geometry}

\allowdisplaybreaks

\begin{document}
    \title{Homework 3 Reflection}
    \author{Ryan Coyne}
    \maketitle
    
    \begin{enumerate}
        \item I could have gone into more detail on this one, but it seems like what I wrote was at least sufficient.
        \item I made the graph so that the deuterium spectrum was behind the hydrogen spectrum. This way, both are visible, rather than the deuterium eclipsing the hydrogen.
        \item I didn't realize that the mass has a small effect on the energy of the photon. That is interesting.
        \item I did the calculations here by hand. It makes sense that you were expecting them to be done in the code.
        \item I just didn't do this one. 
        \item I only plotted the spectrum without matching any lines.
        \item \begin{enumerate}
            \item This one is good!
            \item I forgot that I had to change the radius used in the calculation.
            \item My answers for part b were too high, but I had the right idea here.
            \item I don't really understand what is going on in the frequency part of the table.
        \end{enumerate}
        \item I drew this by hand instead of plotting it on a computer. 
        \item This one I just got correct. I didn't write and calculations because I found it for the previous question.
        \item I don't understand what I did wrong here. I did the same calculation and got the same answer as you. 
    \end{enumerate}
\end{document}